Prefetching SPARQL query cacher

### 2016-05-03 dissertation/cache-proxy.tex
number the messages more on the cache

\documentclass[a4paper, 12pt, draft]{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
%\usepackage{times}
\usepackage{listings}
\usepackage{supertabular}
\usepackage{cite}
\usepackage{amsthm}
\usepackage{tikz}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}
\draw (0,0) --(4,0);
\node at (5.5,0) { Database };
\draw (0,0.5) --(4,0.5);
\node at (5.5,0.5) { Reverse proxy };
\draw (0,2) --(4,2);
\node at (5.5,2) { Caching proxy };
\draw (0,3.5) --(4,3.5);
\node at (5.5,3.5) { Forward proxy };
\draw (0,4) --(4,4);
\node at (5.5,4) { Client cache };

\draw [->] (0.2,4) --(0.2,0);
\draw [<-] (0.4,4) --(0.4,0);
\draw [->] (0.7,2) --(0.7,0);
\draw [<-] (0.9,2) --(0.9,0);
\draw [->] (1.2,4) --(1.2,2);
\draw [dashed, ->] (1.2,2) --(1.2,0);
\draw [dashed, <-] (1.4,2) --(1.4,0);
\draw [->] (1.5,2) --(1.5,4);
\draw [->] (1.7,2) --(1.7,0);
\draw [<-] (1.9,2) --(1.9,0);
\draw [->] (2.2,4) --(2.2,2);
\draw [->] (2.4,2) --(2.4,4);
\end{tikzpicture}
\caption{The possible positions of a cache. A cache may reside at both
  the server side (as a database cache) or client side, or any of the
  intermediate proxies. The arrows illustrate requests (when pointing
  down) and responses (when pointing up) in a deployment scenario for
  when a the query cache considered in this paper is deployed on a
  caching proxy in the Internet infrastructure, see the text for
  details.}\label{fig:messaging}
\end{center}
\end{figure}

@@

My interest is the case where the caching proxy has no further
knowledge of the data than what is exposed through the SPARQL
Endpoint or hypermedia metadata. In practice, there is very
little information.

>>>>

\documentclass[a4paper, 12pt, draft]{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
%\usepackage{times}
\usepackage{listings}
\usepackage{supertabular}
\usepackage{cite}
\usepackage{amsthm}
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}
\draw (0,0) --(4,0);
\node at (5.5,0) { Database };
\draw (0,0.5) --(4,0.5);
\node at (5.5,0.5) { Reverse proxy };
\draw (0,2) --(4,2);
\node at (5.5,2) { Caching proxy };
\draw (0,3.5) --(4,3.5);
\node at (5.5,3.5) { Forward proxy };
\draw (0,4) --(4,4);
\node at (5.5,4) { Client };

\draw [->] (0.2,4) --(0.2,0);
\draw [<-] (0.4,4) --(0.4,0);
\node at (0.3,4.5) {\circled{1}};
\draw [->] (0.7,2) --(0.7,0);
\draw [<-] (0.9,2) --(0.9,0);
\node at (0.8,4.5) {\circled{2}};
\draw [->] (1.2,4) --(1.2,2);
\draw [dashed, ->] (1.2,2) --(1.2,0);
\draw [dashed, <-] (1.4,2) --(1.4,0);
\draw [->] (1.5,2) --(1.5,4);
\node at (1.4,4.5) {\circled{3}};
\draw [->] (1.7,2) --(1.7,0);
\draw [<-] (1.9,2) --(1.9,0);
\node at (1.8,4.5) {\circled{4}};
\draw [->] (2.2,4) --(2.2,2);
\draw [->] (2.4,2) --(2.4,4);
\node at (2.3,4.5) {\circled{5}};
\end{tikzpicture}
\caption{The possible positions of a cache. A cache may reside at both
  the server side (as a database cache) or client side, or any of the
  intermediate proxies. The arrows illustrate requests (when pointing
  down) and responses (when pointing up) in a deployment scenario for
  when a the query cache considered in this paper is deployed on a
  caching proxy in the Internet infrastructure, see the text for
  details.}\label{fig:messaging}
\end{center}
\end{figure}

@@

My interest is the case where the caching proxy has no further
knowledge of the data than what is exposed through the SPARQL Endpoint
or hypermedia metadata. In practice, there is very little
information. If the cache is to be shared, then it would typically
reside on the forward proxy, or in a CDN.

Figure~\ref{fig:messaging} illustrates the case where HTTP messages
are being passed, where the cache is assumed to reside on a
intermediate caching proxy in the Internet, i.e. a CDN. The figure may
be viewed as having time on the $x$-axis, with the arrows pointing
down being requests and the arrows point up being responses. In this
example, the client first makes a request (, which is passed through the
proxy because it has not yet cached any responses. The response is
then also transmitted directly from the SPARQL Endpoint at the
database back to the client. The entire response may be cached at the
proxy in case it can be reused in its entirety. However,
